---
title: "Refugee Analysis"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
runtime: shiny
---

```{r setup, include=FALSE}
library(flexdashboard)
library(highcharter)
library(shiny)
library(FactoMineR)
library(mclust)
library(tidyr)
library(dplyr)
library(PCAmixdata)
library(DT)

categorical <- c("Continent","Region","Country","Area","Longitude","Latitude","Climate","Reason","Planning",'Access','Management','Main occupation','Shelter','Health Facility (Hospital)','Health Facility (Clinic)','Education Facility (Primary School)','Education Facility (Secondary School)','Community Facility (Recreation, Social)','Distribution Centre','Commerce','Industry','Power','Water','Sanitation','Communication (Internet, mobile phone)','Other infrastructure')

numerical <- c("Lifespan (years)", "Density  (People/km2)", "Area  (m2/person)","Size (km2)", "Population", "Density", "Percentage_Male", "Percentage_Female", "Percentage_0 to 11", "Percentage_12 to 17", "Percentage_18 to 59", "Percentage _60 plus", "Average Temperature (Celsius)", "Average Rain (mm)")

groups <- list(Location = c("Continent", "Region", "Country", "Area", "Longitude", "Latitude"),
               Climate = c("Climate", "Average Temperature (Celsius)", "Average Rain (mm)"),
               Lifespan = c("Lifespan (years)"), 
               Population = c("Population"), 
               Density = c("Density  (People/km2)","Area  (m2/person)","Size (km2)"),
               Demographics = c("Percentage_Male", "Percentage_Female", "Percentage_0 to 11", "Percentage_12 to 17", "Percentage_18 to 59", "Percentage _60 plus"),
               Logistics = c("Planning",'Access','Management'),
               Infrastructure = c('Health Facility (Hospital)','Health Facility (Clinic)','Education Facility (Primary School)','Education Facility (Secondary School)','Community Facility (Recreation, Social)','Power','Water','Communication (Internet, mobile phone)','Other infrastructure','Sanitation'),
               Development = c('Distribution Centre','Commerce','Industry','Main occupation','Shelter')
               )


other_groups <- list(Location = c("Continent", "Region", "Country", "Area", "Longitude", "Latitude"),
               Climate = c("Climate", "Average Temperature (Celsius)", "Average Rain (mm)"),
               Lifespan = c("Lifespan (years)"), 
               Population = c("Population"), 
               Density = c("Density  (People/km2)","Area  (m2/person)","Size (km2)"),
               Demographics = c("Percentage_Male", "Percentage_Female", "Percentage_0 to 11", "Percentage_12 to 17", "Percentage_18 to 59", "Percentage _60 plus"),
               Logistics = c("Planning",'Management')
               )  
  



area_groups <- list(Location = c("Continent", "Region", "Country", "Longitude", "Latitude"),
               Climate = c("Climate", "Average Temperature (Celsius)", "Average Rain (mm)"),
               Lifespan = c("Lifespan (years)"), 
               Population = c("Population"), 
               Density = c("Density  (People/km2)","Area  (m2/person)","Size (km2)"), 
               Demographics = c("Percentage_Male", "Percentage_Female", "Percentage_0 to 11", "Percentage_12 to 17", "Percentage_18 to 59", "Percentage _60 plus"),
               Logistics = c("Planning",'Management'),
               Infrastructure = c('Health Facility (Hospital)','Health Facility (Clinic)','Education Facility (Primary School)','Education Facility (Secondary School)','Community Facility (Recreation, Social)','Power','Water','Sanitation'),
               Development = c('Distribution Centre','Commerce','Industry','Main occupation','Shelter')
               )  
  

refugee <- readxl::read_xlsx("./Refugee Camp Data Analysis (working file) - Copy v4.xlsx")

proper_refugee_data<-refugee[,which(colnames(refugee) %in% categorical)]
numerical_refugee_data<-refugee[,which(colnames(refugee) %in% numerical)]


ID_refugee_camp <- refugee$`Accommodation Type`==c("Refugee Camp")
ID_IDP_settlement <- refugee$`Accommodation Type`==c("IDP Settlement")
ID_community_settlement <- refugee$`Accommodation Type`==c("Community Settlement")
ID_status_open <- refugee$Condition == c("Open")
ID_status_open_rural <- refugee$Condition == c("Open") & refugee$Area == c("Rural")
ID_status_open_all_urban <- refugee$Condition == c("Open") & ( refugee$Area == c("Semi-urban") |  refugee$Area == c("Urban") )
ID_status_closed <- refugee$Condition == c("Closed")



data__refugee_camp___status_open<-cbind(numerical_refugee_data[as.logical(ID_refugee_camp*ID_status_open),],proper_refugee_data[as.logical(ID_refugee_camp*ID_status_open),])



MCA___refugee_camp___status_open<-PCAmixdata::MFAmix(data = data__refugee_camp___status_open[,do.call('c',lapply(groups,function(X){
  which(colnames(data__refugee_camp___status_open) %in% X)
}))],ndim = 2,rename.level = T,groups = c(do.call('c',lapply(c(1:length(groups)),function(X){
  rep(X,length(groups[[X]]))
}))),name.groups = c(names(groups)),graph = F)




data__refugee_camp___status_open_rural<-cbind(numerical_refugee_data[as.logical(ID_refugee_camp*ID_status_open_rural),],proper_refugee_data[as.logical(ID_refugee_camp*ID_status_open_rural),])


data__refugee_camp___status_open_rural = data__refugee_camp___status_open_rural[,-17]


MCA___refugee_camp___status_open_rural<-PCAmixdata::MFAmix(data = data__refugee_camp___status_open_rural[,do.call('c',lapply(area_groups,function(X){
  which(colnames(data__refugee_camp___status_open_rural) %in% X)
}))],ndim = 2,rename.level = T,groups = c(do.call('c',lapply(c(1:length(area_groups)),function(X){
  rep(X,length(area_groups[[X]]))
}))),name.groups = c(names(area_groups)),graph = F)








data__refugee_camp___status_open_all_urban<-cbind(numerical_refugee_data[as.logical(ID_refugee_camp*ID_status_open_all_urban),],proper_refugee_data[as.logical(ID_refugee_camp*ID_status_open_all_urban),])


data__refugee_camp___status_open_all_urban = data__refugee_camp___status_open_all_urban[,which(apply(data__refugee_camp___status_open_all_urban,2,function(X){length(unique(X))})>1)]

MCA___refugee_camp___status_open_all_urban<-PCAmixdata::MFAmix(data = data__refugee_camp___status_open_all_urban[,do.call('c',lapply(area_groups,function(X){
  which(colnames(data__refugee_camp___status_open_all_urban) %in% X)
}))],ndim = 2,rename.level = T,groups = c(do.call('c',lapply(c(1:length(area_groups)),function(X){
  rep(X,length(area_groups[[X]]))
}))),name.groups = c(names(area_groups)),graph = F)






data__refugee_camp___status_closed<-cbind(numerical_refugee_data[as.logical(ID_refugee_camp*ID_status_closed),],proper_refugee_data[as.logical(ID_refugee_camp*ID_status_closed),])



MCA___refugee_camp___status_closed<-PCAmixdata::MFAmix(data = data__refugee_camp___status_closed[,do.call('c',lapply(other_groups,function(X){
  which(colnames(data__refugee_camp___status_closed) %in% X)
}))],ndim = 2,rename.level = T,groups = c(do.call('c',lapply(c(1:length(other_groups)),function(X){
  rep(X,length(other_groups[[X]]))
}))),name.groups = c(names(other_groups)),graph = F)





data__refugee_camp___status_all<-cbind(numerical_refugee_data[as.logical(ID_refugee_camp),],proper_refugee_data[as.logical(ID_refugee_camp),])



MCA___refugee_camp___status_all<-PCAmixdata::MFAmix(data = data__refugee_camp___status_all[,do.call('c',lapply(other_groups,function(X){
  which(colnames(data__refugee_camp___status_all) %in% X)
}))],ndim = 2,rename.level = T,groups = c(do.call('c',lapply(c(1:length(other_groups)),function(X){
  rep(X,length(other_groups[[X]]))
}))),name.groups = c(names(other_groups)),graph = F)



data__IDP_settlement___status_all<-cbind(numerical_refugee_data[as.logical(ID_IDP_settlement),],proper_refugee_data[as.logical(ID_IDP_settlement),])



MCA___IDP_settlement___status_all<-PCAmixdata::MFAmix(data = data__IDP_settlement___status_all[,do.call('c',lapply(other_groups,function(X){
  which(colnames(data__IDP_settlement___status_all) %in% X)
}))],ndim = 2,rename.level = T,groups = c(do.call('c',lapply(c(1:length(other_groups)),function(X){
  rep(X,length(other_groups[[X]]))
}))),name.groups = c(names(other_groups)),graph = F)



data__community_settlement___status_all<-cbind(numerical_refugee_data[as.logical(ID_community_settlement),],proper_refugee_data[as.logical(ID_community_settlement),])



MCA___community_settlement___status_all<-PCAmixdata::MFAmix(data = data__community_settlement___status_all[,do.call('c',lapply(other_groups,function(X){
  which(colnames(data__community_settlement___status_all) %in% X)
}))],ndim = 2,rename.level = T,groups = c(do.call('c',lapply(c(1:length(other_groups)),function(X){
  rep(X,length(other_groups[[X]]))
}))),name.groups = c(names(other_groups)),graph = F)


# save.image("./main.Rdata")


# load("./main.Rdata")


```



Refugee Camp
=======================================================================
Inputs {.sidebar}
-------------------------------------
```{r}
selectInput(inputId = "status_variables",
                   label = "Status",
            choices = c("All","Open","Open-Rural","Open-Not Rural","Closed"))

selectInput(inputId = "factor_variable1",
                   label = "Factor of Interest",
            choices = c("Lifespan","Density"))

```

Row {data-height=500} 
-------------------------------------

### How do the variables correlate with my Factor of interest?

```{r}

  renderHighchart({

    using_data <- MCA___refugee_camp___status_all
    id_selection <- rep(T,length(ID_refugee_camp))

    if (input$status_variables=="Open"){
      using_data <- MCA___refugee_camp___status_open
      id_selection <- as.logical(ID_status_open*ID_refugee_camp)
    }
    if (input$status_variables=="Open-Rural"){
      using_data <- MCA___refugee_camp___status_open_rural
      id_selection <- as.logical(ID_status_open_rural*ID_refugee_camp)
    }
    if (input$status_variables=="Open-Not Rural"){
      using_data <- MCA___refugee_camp___status_open_all_urban
      id_selection <- as.logical(ID_status_open_all_urban*ID_refugee_camp)
    }
    if (input$status_variables=="Closed"){
      using_data <- MCA___refugee_camp___status_closed
      id_selection <- as.logical(ID_status_closed*ID_refugee_camp)
    }
    if (input$status_variables=="All"){
      using_data <- MCA___refugee_camp___status_all
      id_selection <- as.logical(ID_refugee_camp)
    }


    if(input$factor_variable1=="Lifespan"){
      type_factor<-"Lifespan..years."
    }
    if(input$factor_variable1=="Density"){
      type_factor<-"Density...People.km2."
    }


    data_MCA<-as.matrix(proxy::simil(using_data[["quanti"]][["coord"]],"cosine"))
    data_MCA<-data.frame(data_MCA)
    main <- data.frame(Names=colnames(data_MCA)[-which(colnames(data_MCA)==type_factor)],Correlation=data_MCA[-which(colnames(data_MCA)==type_factor),which(colnames(data_MCA)==type_factor)])
    main<-main[order(as.numeric(main[,2])),]

      main<-main[which(!c(main$Names%in%groups$Location | main$Names%in%groups$Climate | grepl(pattern = c("*Temperature*|*Rain*"),main$Names))),]

    main$Direction<-as.numeric(main[,2])>=0
    main$Direction[main$Direction==F]<-c("Below")
    main$Direction[main$Direction==T]<-c("Above")

    main_1 <- main[which(main$Names %in% c("Lifespan..years.","Population","Density...People.km2.","Area...m2.person.","Size..km2.")),]
    # main_2 <- main[which(main$Names %in% c("Percentage_Male","Percentage_Female")),]
    main_3 <- main[which(main$Names %in% c("Percentage_0.to.11","Percentage_12.to.17","Percentage_18.to.59","Percentage._60.plus")),]
    main_space <- rep(0,dim(main)[2])

    main <- rbind(main_1,
                  main_space,
                  # main_2,
                  # main_space,
                  main_3)

    main$Order<-c(1:dim(main)[1])

  hc <- hchart(main,type="column",hcaes(y=Correlation,x=Order,group=Direction,grvar=Names),dataLabels = list(enabled = TRUE, format='{point.grvar}'),showInLegend=F) %>% hc_tooltip(pointFormat = "{point.grvar}") %>% hc_xAxis(visible=F)


  hc

  }) 


```


### Which overall group contributes to my Factor of interest the most?
```{r}

  renderHighchart({

    using_data <- MCA___refugee_camp___status_all
    id_selection <- rep(T,length(ID_refugee_camp))

    if (input$status_variables=="Open"){
      using_data <- MCA___refugee_camp___status_open
      id_selection <- as.logical(ID_status_open*ID_refugee_camp)
    }
    if (input$status_variables=="Open-Rural"){
      using_data <- MCA___refugee_camp___status_open_rural
      id_selection <- as.logical(ID_status_open_rural*ID_refugee_camp)
    }
    if (input$status_variables=="Open-Not Rural"){
      using_data <- MCA___refugee_camp___status_open_all_urban
      id_selection <- as.logical(ID_status_open_all_urban*ID_refugee_camp)
    }
    if (input$status_variables=="Closed"){
      using_data <- MCA___refugee_camp___status_closed
      id_selection <- as.logical(ID_status_closed*ID_refugee_camp)
    }
    if (input$status_variables=="All"){
      using_data <- MCA___refugee_camp___status_all
      id_selection <- as.logical(ID_refugee_camp)
    }


    data_MCA<-as.matrix(cor(do.call('cbind',lapply(using_data[["ind.partial"]],function(X){X[,1]}))))
    data_MCA<-data.frame(data_MCA)
    main <- data.frame(Names=colnames(data_MCA)[-which(colnames(data_MCA)==input$factor_variable1)],Contribution=data_MCA[-which(colnames(data_MCA)==input$factor_variable1),which(colnames(data_MCA)==input$factor_variable1)])
    main<-main[order(as.numeric(main[,2])),]

    main$Direction<-as.numeric(main[,2])>=0
    main$Direction[main$Direction==F]<-c("Below")
    main$Direction[main$Direction==T]<-c("Above")

    main$Order<-as.character(letters[c(1:dim(main)[1])])

    main$SubGroups <- do.call('c',lapply(main$Names,function(X){
      paste0(groups[[which(names(groups)==X)]],collapse=" ; ")
    }))

  hc <- hchart(main,type="bar",hcaes(y=Contribution,group=Order,grvar=Names,col=Names,label=SubGroups),dataLabels = list(enabled = TRUE, format='{point.grvar}'),showInLegend=F,column = list(stacking = "normal")) %>%
hc_tooltip(pointFormat = "{point.label}") %>% hc_xAxis(visible=F)

  hc
  }) 


```


Row {data-height=500} 
-------------------------------------




### Barplot ranking the most similar to my Factor of interest?
```{r}

  renderHighchart({

    using_data <- MCA___refugee_camp___status_all
    id_selection <- rep(T,length(ID_refugee_camp))

    if (input$status_variables=="Open"){
      using_data <- MCA___refugee_camp___status_open
      id_selection <- as.logical(ID_status_open*ID_refugee_camp)
    }
    if (input$status_variables=="Open-Rural"){
      using_data <- MCA___refugee_camp___status_open_rural
      id_selection <- as.logical(ID_status_open_rural*ID_refugee_camp)
    }
    if (input$status_variables=="Open-Not Rural"){
      using_data <- MCA___refugee_camp___status_open_all_urban
      id_selection <- as.logical(ID_status_open_all_urban*ID_refugee_camp)
    }
    if (input$status_variables=="Closed"){
      using_data <- MCA___refugee_camp___status_closed
      id_selection <- as.logical(ID_status_closed*ID_refugee_camp)
    }
    if (input$status_variables=="All"){
      using_data <- MCA___refugee_camp___status_all
      id_selection <- as.logical(ID_refugee_camp)
    }


    if(input$factor_variable1=="Lifespan"){
      type_factor<-"Lifespan..years."
    }
    if(input$factor_variable1=="Density"){
      type_factor<-"Density...People.km2."
    }

    data_MCA<-data.frame(Similarity = sort(using_data[["sqload"]][,1],decreasing = T))

    names_MCA = row.names(data_MCA)[which(!c(row.names(data_MCA)%in%groups$Location | row.names(data_MCA)%in%groups$Climate | grepl(pattern = c("*Temperature*|*Rain*"),row.names(data_MCA))))]
    data_MCA<-data.frame(Similarity=data_MCA[which(!c(row.names(data_MCA)%in%groups$Location | row.names(data_MCA)%in%groups$Climate | grepl(pattern = c("*Temperature*|*Rain*"),row.names(data_MCA)))),])
    row.names(data_MCA)<-names_MCA
    
    data_MCA <- round(data_MCA,3)

    main<-data_MCA[order(data_MCA$Similarity,decreasing = T)[1:6],1]
    main_names<-row.names(data_MCA)[order(data_MCA$Similarity,decreasing = T)[1:6]]
    
    main<-data.frame(Similarity=main,Names=main_names)
    main$Order<-as.character(letters[c(1:dim(main)[1])])
    
  hc <- hchart(main,type="bar",hcaes(y=Similarity,group=Order,grvar=Names,col=Names),dataLabels = list(enabled = TRUE, format='{point.grvar}'),showInLegend=F,column = list(stacking = "normal")) %>%
hc_tooltip(pointFormat = "{point.grvar}") %>% hc_xAxis(visible=F)

  hc
  }) 


```


### Table ranking the most similar to my Factor of interest?
```{r}


    DT::renderDataTable({


    using_data <- MCA___refugee_camp___status_all
    id_selection <- rep(T,length(ID_refugee_camp))

    if (input$status_variables=="Open"){
      using_data <- MCA___refugee_camp___status_open
      id_selection <- as.logical(ID_status_open*ID_refugee_camp)
    }
    if (input$status_variables=="Open-Rural"){
      using_data <- MCA___refugee_camp___status_open_rural
      id_selection <- as.logical(ID_status_open_rural*ID_refugee_camp)
    }
    if (input$status_variables=="Open-Not Rural"){
      using_data <- MCA___refugee_camp___status_open_all_urban
      id_selection <- as.logical(ID_status_open_all_urban*ID_refugee_camp)
    }
    if (input$status_variables=="Closed"){
      using_data <- MCA___refugee_camp___status_closed
      id_selection <- as.logical(ID_status_closed*ID_refugee_camp)
    }
    if (input$status_variables=="All"){
      using_data <- MCA___refugee_camp___status_all
      id_selection <- as.logical(ID_refugee_camp)
    }


    if(input$factor_variable1=="Lifespan"){
      type_factor<-"Lifespan..years."
    }
    if(input$factor_variable1=="Density"){
      type_factor<-"Density...People.km2."
    }

    data_MCA<-data.frame(Similarity = sort(using_data[["sqload"]][,1],decreasing = T))
    

    names_MCA = row.names(data_MCA)[which(!c(row.names(data_MCA)%in%groups$Location | row.names(data_MCA)%in%groups$Climate | grepl(pattern = c("*Temperature*|*Rain*"),row.names(data_MCA))))]
    data_MCA<-data.frame(Similarity=data_MCA[which(!c(row.names(data_MCA)%in%groups$Location | row.names(data_MCA)%in%groups$Climate | grepl(pattern = c("*Temperature*|*Rain*"),row.names(data_MCA)))),])
    row.names(data_MCA)<-names_MCA
    
    data_MCA <- round(data_MCA,3)

    DT::datatable(data_MCA,fillContainer=T)
    
    })
    
  

```
























IDP Settlement
=======================================================================
Inputs {.sidebar}
-------------------------------------
```{r}

selectInput(inputId = "factor_variable2",
                   label = "Factor of Interest",
            choices = c("Lifespan","Density"))

```

Row {data-height=500} 
-------------------------------------

### How do the variables correlate with my Factor of interest?

```{r}

  renderHighchart({

    using_data <- MCA___IDP_settlement___status_all
    id_selection <- rep(T,length(ID_IDP_settlement))

    if(input$factor_variable2=="Lifespan"){
      type_factor<-"Lifespan..years."
    }
    if(input$factor_variable2=="Density"){
      type_factor<-"Density...People.km2."
    }

    data_MCA<-as.matrix(proxy::simil(using_data[["quanti"]][["coord"]],"cosine"))
    data_MCA<-data.frame(data_MCA)
    main <- data.frame(Names=colnames(data_MCA)[-which(colnames(data_MCA)==type_factor)],Correlation=data_MCA[-which(colnames(data_MCA)==type_factor),which(colnames(data_MCA)==type_factor)])
    main<-main[order(as.numeric(main[,2])),]

      main<-main[which(!c(main$Names%in%groups$Location | main$Names%in%groups$Climate | grepl(pattern = c("*Temperature*|*Rain*"),main$Names))),]

    main$Direction<-as.numeric(main[,2])>=0
    main$Direction[main$Direction==F]<-c("Below")
    main$Direction[main$Direction==T]<-c("Above")


    main_1 <- main[which(main$Names %in% c("Lifespan..years.","Population","Density...People.km2.","Area...m2.person.","Size..km2.")),]
    # main_2 <- main[which(main$Names %in% c("Percentage_Male","Percentage_Female")),]
    main_3 <- main[which(main$Names %in% c("Percentage_0.to.11","Percentage_12.to.17","Percentage_18.to.59","Percentage._60.plus")),]
    main_space <- rep(0,dim(main)[2])

    main <- rbind(main_1,
                  main_space,
                  # main_2,
                  # main_space,
                  main_3)


    main$Order<-c(1:dim(main)[1])

  hc <- hchart(main,type="column",hcaes(y=Correlation,x=Order,group=Direction,grvar=Names),dataLabels = list(enabled = TRUE, format='{point.grvar}'),showInLegend=F) %>% hc_tooltip(pointFormat = "{point.grvar}") %>% hc_xAxis(visible=F)


  hc

  }) 


```


### Which overall group contributes to my Factor of interest the most?
```{r}

  renderHighchart({


    using_data <- MCA___IDP_settlement___status_all
    id_selection <- rep(T,length(ID_IDP_settlement))

    data_MCA<-as.matrix(cor(do.call('cbind',lapply(using_data[["ind.partial"]],function(X){X[,1]}))))
    data_MCA<-data.frame(data_MCA)
    main <- data.frame(Names=colnames(data_MCA)[-which(colnames(data_MCA)==input$factor_variable2)],Contribution=data_MCA[-which(colnames(data_MCA)==input$factor_variable2),which(colnames(data_MCA)==input$factor_variable2)])
    main<-main[order(as.numeric(main[,2])),]

    main$Direction<-as.numeric(main[,2])>=0
    main$Direction[main$Direction==F]<-c("Below")
    main$Direction[main$Direction==T]<-c("Above")

    main$Order<-as.character(letters[c(1:dim(main)[1])])


    main$SubGroups <- do.call('c',lapply(main$Names,function(X){
      paste0(groups[[which(names(groups)==X)]],collapse=" ; ")
    }))

  hc <- hchart(main,type="bar",hcaes(y=Contribution,group=Order,grvar=Names,col=Names,label=SubGroups),dataLabels = list(enabled = TRUE, format='{point.grvar}'),showInLegend=F,column = list(stacking = "normal")) %>%
hc_tooltip(pointFormat = "{point.label}") %>% hc_xAxis(visible=F)

  hc
  }) 


```




Row {data-height=500} 
-------------------------------------



### Barplot ranking the most similar to my Factor of interest?
```{r}

  renderHighchart({


    using_data <- MCA___IDP_settlement___status_all
    id_selection <- rep(T,length(ID_IDP_settlement))

    if(input$factor_variable2=="Lifespan"){
      type_factor<-"Lifespan..years."
    }
    if(input$factor_variable2=="Density"){
      type_factor<-"Density...People.km2."
    }


    data_MCA<-data.frame(Similarity = sort(using_data[["sqload"]][,1],decreasing = T))

    names_MCA = row.names(data_MCA)[which(!c(row.names(data_MCA)%in%groups$Location | row.names(data_MCA)%in%groups$Climate | grepl(pattern = c("*Temperature*|*Rain*"),row.names(data_MCA))))]
    data_MCA<-data.frame(Similarity=data_MCA[which(!c(row.names(data_MCA)%in%groups$Location | row.names(data_MCA)%in%groups$Climate | grepl(pattern = c("*Temperature*|*Rain*"),row.names(data_MCA)))),])
    row.names(data_MCA)<-names_MCA
    
    data_MCA <- round(data_MCA,3)

    main<-data_MCA[order(data_MCA$Similarity,decreasing = T)[1:6],1]
    main_names<-row.names(data_MCA)[order(data_MCA$Similarity,decreasing = T)[1:6]]
    
    main<-data.frame(Similarity=main,Names=main_names)
    main$Order<-as.character(letters[c(1:dim(main)[1])])
    
  hc <- hchart(main,type="bar",hcaes(y=Similarity,group=Order,grvar=Names,col=Names),dataLabels = list(enabled = TRUE, format='{point.grvar}'),showInLegend=F,column = list(stacking = "normal")) %>%
hc_tooltip(pointFormat = "{point.grvar}") %>% hc_xAxis(visible=F)

  hc
  }) 


```


### Table ranking the most similar to my Factor of interest?
```{r}


    DT::renderDataTable({

    using_data <- MCA___IDP_settlement___status_all
    id_selection <- rep(T,length(ID_IDP_settlement))

    if(input$factor_variable2=="Lifespan"){
      type_factor<-"Lifespan..years."
    }
    if(input$factor_variable2=="Density"){
      type_factor<-"Density...People.km2."
    }


    data_MCA<-data.frame(Similarity = sort(using_data[["sqload"]][,1],decreasing = T))

    names_MCA = row.names(data_MCA)[which(!c(row.names(data_MCA)%in%groups$Location | row.names(data_MCA)%in%groups$Climate | grepl(pattern = c("*Temperature*|*Rain*"),row.names(data_MCA))))]
    data_MCA<-data.frame(Similarity=data_MCA[which(!c(row.names(data_MCA)%in%groups$Location | row.names(data_MCA)%in%groups$Climate | grepl(pattern = c("*Temperature*|*Rain*"),row.names(data_MCA)))),])
    row.names(data_MCA)<-names_MCA
    
    data_MCA <- round(data_MCA,3)

    DT::datatable(data_MCA,fillContainer=T)

    })

```


























Community Settlement
=======================================================================
Inputs {.sidebar}
-------------------------------------
```{r}

selectInput(inputId = "factor_variable3",
                   label = "Factor of Interest",
            choices = c("Lifespan","Density"))

```

Row {data-height=500} 
-------------------------------------

### How do the variables correlate with my Factor of interest?

```{r}

  renderHighchart({

    using_data <- MCA___community_settlement___status_all
    id_selection <- rep(T,length(ID_community_settlement))

    if(input$factor_variable3=="Lifespan"){
      type_factor<-"Lifespan..years."
    }
    if(input$factor_variable3=="Density"){
      type_factor<-"Density...People.km2."
    }

    data_MCA<-as.matrix(proxy::simil(using_data[["quanti"]][["coord"]],"cosine"))
    data_MCA<-data.frame(data_MCA)
    main <- data.frame(Names=colnames(data_MCA)[-which(colnames(data_MCA)==type_factor)],Correlation=data_MCA[-which(colnames(data_MCA)==type_factor),which(colnames(data_MCA)==type_factor)])
    main<-main[order(as.numeric(main[,2])),]


      main<-main[which(!c(main$Names%in%groups$Location | main$Names%in%groups$Climate | grepl(pattern = c("*Temperature*|*Rain*"),main$Names))),]

    main$Direction<-as.numeric(main[,2])>=0
    main$Direction[main$Direction==F]<-c("Below")
    main$Direction[main$Direction==T]<-c("Above")
    
    print(main$Names)
    
    main_1 <- main[which(main$Names %in% c("Lifespan..years.","Population","Density...People.km2.","Area...m2.person.","Size..km2.")),]
    # main_2 <- main[which(main$Names %in% c("Percentage_Male","Percentage_Female")),]
    main_3 <- main[which(main$Names %in% c("Percentage_0.to.11","Percentage_12.to.17","Percentage_18.to.59","Percentage._60.plus")),]
    main_space <- rep(0,dim(main)[2])

    main <- rbind(main_1,
                  main_space,
                  # main_2,
                  # main_space,
                  main_3)

    main$Order<-c(1:dim(main)[1])

  hc <- hchart(main,type="column",hcaes(y=Correlation,x=Order,group=Direction,grvar=Names),dataLabels = list(enabled = TRUE, format='{point.grvar}'),showInLegend=F) %>% hc_tooltip(pointFormat = "{point.grvar}") %>% hc_xAxis(visible=F)


  hc

  }) 


```

### Which overall group contributes to my Factor of interest the most?
```{r}

  renderHighchart({


    using_data <- MCA___community_settlement___status_all
    id_selection <- rep(T,length(ID_community_settlement))


    data_MCA<-as.matrix(cor(do.call('cbind',lapply(using_data[["ind.partial"]],function(X){X[,1]}))))
    data_MCA<-data.frame(data_MCA)
    main <- data.frame(Names=colnames(data_MCA)[-which(colnames(data_MCA)==input$factor_variable3)],Contribution=data_MCA[-which(colnames(data_MCA)==input$factor_variable3),which(colnames(data_MCA)==input$factor_variable3)])
    main<-main[order(as.numeric(main[,2])),]

    main$Direction<-as.numeric(main[,2])>=0
    main$Direction[main$Direction==F]<-c("Below")
    main$Direction[main$Direction==T]<-c("Above")

    main$Order<-as.character(letters[c(1:dim(main)[1])])


    main$SubGroups <- do.call('c',lapply(main$Names,function(X){
      paste0(groups[[which(names(groups)==X)]],collapse=" ; ")
    }))

  hc <- hchart(main,type="bar",hcaes(y=Contribution,group=Order,grvar=Names,col=Names,label=SubGroups),dataLabels = list(enabled = TRUE, format='{point.grvar}'),showInLegend=F,column = list(stacking = "normal")) %>%
hc_tooltip(pointFormat = "{point.label}") %>% hc_xAxis(visible=F)

  hc
  }) 


```





Row {data-height=500} 
-------------------------------------


### Barplot ranking the most similar to my Factor of interest?
```{r}

  renderHighchart({


    using_data <- MCA___community_settlement___status_all
    id_selection <- rep(T,length(ID_community_settlement))


    if(input$factor_variable3=="Lifespan"){
      type_factor<-"Lifespan..years."
    }
    if(input$factor_variable3=="Density"){
      type_factor<-"Density...People.km2."
    }


    data_MCA<-data.frame(Similarity = sort(using_data[["sqload"]][,1],decreasing = T))

    names_MCA = row.names(data_MCA)[which(!c(row.names(data_MCA)%in%groups$Location | row.names(data_MCA)%in%groups$Climate | grepl(pattern = c("*Temperature*|*Rain*"),row.names(data_MCA))))]
    data_MCA<-data.frame(Similarity=data_MCA[which(!c(row.names(data_MCA)%in%groups$Location | row.names(data_MCA)%in%groups$Climate | grepl(pattern = c("*Temperature*|*Rain*"),row.names(data_MCA)))),])
    row.names(data_MCA)<-names_MCA
    
    data_MCA <- round(data_MCA,3)

    main<-data_MCA[order(data_MCA$Similarity,decreasing = T)[1:6],1]
    main_names<-row.names(data_MCA)[order(data_MCA$Similarity,decreasing = T)[1:6]]
    
    main<-data.frame(Similarity=main,Names=main_names)
    main$Order<-as.character(letters[c(1:dim(main)[1])])
    
  hc <- hchart(main,type="bar",hcaes(y=Similarity,group=Order,grvar=Names,col=Names),dataLabels = list(enabled = TRUE, format='{point.grvar}'),showInLegend=F,column = list(stacking = "normal")) %>%
hc_tooltip(pointFormat = "{point.grvar}") %>% hc_xAxis(visible=F)

  hc
  }) 


```


### Table ranking the most similar to my Factor of interest?
```{r}



 
    DT::renderDataTable({


    using_data <- MCA___community_settlement___status_all
    id_selection <- rep(T,length(ID_community_settlement))


    if(input$factor_variable3=="Lifespan"){
      type_factor<-"Lifespan..years."
    }
    if(input$factor_variable3=="Density"){
      type_factor<-"Density...People.km2."
    }


    data_MCA<-data.frame(Similarity = sort(using_data[["sqload"]][,1],decreasing = T))

    names_MCA = row.names(data_MCA)[which(!c(row.names(data_MCA)%in%groups$Location | row.names(data_MCA)%in%groups$Climate | grepl(pattern = c("*Temperature*|*Rain*"),row.names(data_MCA))))]
    data_MCA<-data.frame(Similarity=data_MCA[which(!c(row.names(data_MCA)%in%groups$Location | row.names(data_MCA)%in%groups$Climate | grepl(pattern = c("*Temperature*|*Rain*"),row.names(data_MCA)))),])
    row.names(data_MCA)<-names_MCA
    
    data_MCA <- round(data_MCA,3)

    DT::datatable(data_MCA,fillContainer=T)

    })
  

```

